A Journey from Wild to Textbook Data to Reproducibly Refresh the Wages Data from the National Longitudinal Survey of Youth Database

### 2022-05-12 paper/paper.Rmd
changed first data print so that it fits into page, and the paragraph on race matching

Lastly, the race variable is almost perfectly matched. The `id`'s in the dropouts subset of the refreshed data all correspond to males, which perfectly matches the original subset.

>>>>

Lastly, the matching of individuals in the dropouts subset of the refreshed data with the original data was done using their `id`s. (Only males were in the original data.) It was comforting to see that all of the individuals in both sets do match on sex (all are male!), and race.
